\beginsong{Imagine}[by={John Lennon}]
\beginverse
\[C]Imagine there's no \[Cmaj7]hea\[F]ven
\[C]It's easy if you \[Cmaj7]tr\[F]y
\[C]No hell be\[Cmaj7]low \[F]us
\[C]Above us only \[Cmaj7]sk\[F]y
\[F]Imagine \[Am/E]all the \[Dm7]people \[F/C]
\[G]Living for to\[C/G]da\[G7]y, a-hah
\endverse
\beginverse
\[C]Imagine there's no \[Cmaj7]coun\[F]tries
\[C]It isn't hard to \[Cmaj7]d\[F]o
\[C]Nothing to kill or \[Cmaj7]die \[F]for
\[C]And no religion \[Cmaj7]to\[F]o
\[F]Imagine \[Am/E]all the \[Dm7]people \[F/C]
\[G]Living life in \[C/G]pea\[G7]ce, you
\endverse
\beginchorus
\[F]You may \[G]say I'm a \[C]dream\[Cmaj7]er \[E] \[E7]
\[F]But I'm not the \[G]only \[C]one \[Cmaj7] \[E] \[E7]
\[F]I hope some\[G]day you'll \[C]join \[Cmaj7]us \[E] \[E7]
\[F]And the \[G]world will be as \[C]one
\endchorus
\beginverse
\[C]Imagine no pos\[Cmaj7]ses\[F]sions
\[C]I wonder if you \[Cmaj7]ca\[F]n
\[C]No need for greed or \[Cmaj7]hun\[F]ger
\[C]A brotherhood of \[Cmaj7]ma\[F]n
\[F]Imagine \[Am/E]all the \[Dm7]people \[F/C]
\[G]Sharing all the \[C/G]wor\[G7]ld, you
\endverse
\endsong

\beginsong{I'm Yours}[by={Jason Mraz}]
\textnote{Capo 4}
\beginverse
\[G]Well you done done me in, you bet I felt it
\[D]I tried to be chill but you're so hot that I melted
\[Em]I fell right through the cracks
\[C]Now I'm tryin' to get back
\[G]Before the cool done run out I'll be givin' it my bestest
\[D]And nothin's gonna stop me but divine intervention
\[Em]I reckon it's again my turn
\[C]To win some or learn some
\endverse
\beginchorus
\[G]But I won't hesi\[D]tate no more, no \[Em]more
It cannot \[C]wait, I'm yours
\endchorus
\beginverse
\[G]Well open up your mind and see like \[D]me
Open up your plans and damn you're \[Em]free
Look into your heart and you'll find \[C]love love love love
\[G]Listen to the music of the moment, people dance and \[D]sing
We're just one big fami\[Em]ly
And it's our God-forsaken right to be \[C]loved loved loved loved \[A7]loved
\endverse
\beginchorus
\[G]So I won't hesi\[D]tate \[Dsus4]no more, no \[Em]more
It cannot \[C]wait, I'm sure
There's no \[G]need to compli\[D]cate, our time is \[Em]short
This is our \[C]fate, I'm yours
\endchorus
\beginverse*
\[G]Doo do do doo doo \[D]do, doo do doo do \[Em]doo do
Do you want to come on, \[D]scooch on over \[C]closer, dear
And I will nibble your \[A7]ear
\endverse*
\beginverse
\[G]I've been spending way too long checking my tongue in the mirror
\[D]And bending over backwards just to try to see it clearer
\[Em]But my breath fogged up the glass
\[C]And so I drew a new face and I laughed
\[G]I guess what I'll be saying is there ain't no better reason
\[D]To rid yourself of vanities and just go with the seasons
\[Em]It's what we aim to do
\[C]Our name is our virtue
\endverse
\endsong

\beginsong{Lemon Tree}[by={Fool's Garden}]
\textnote{Capo 8}
\beginverse
\[Am]I'm sitting here in a \[Em]boring room,
\[Am]It's just another rainy \[Em]Sunday afternoon.
\[Am]I'm wasting my time, I got \[Em]nothing to do.
\[Am]I'm hanging around, I'm \[Em]waiting for you,
\[Dm]But nothing ever \[Em]happens and I \[Am]wonder.
\endverse
\beginverse
\[Am]I'm driving around in my \[Em]car,
\[Am]I'm driving too fast, I'm \[Em]driving too far.
\[Am]I'd like to change my \[Em]point of view,
\[Am]I feel so lonely, I'm \[Em]waiting for you,
\[Dm]But nothing ever \[Em]happens and I \[Am]wonder.
\endverse
\beginchorus
\[C]I wonder how, I wonder \[G]why,
\[Am]Yesterday you told me 'bout the \[Em]blue blue sky
\[F]And all that I can \[G]see is just a yellow \[C]lemon \[G7]tree.
\[C]I'm turning my head, up \[G]and down,
\[Am]I'm turning, turning, turning, turning, \[Em]turning around
\[F]And all that I can \[F#dim7]see is just another \[G]lemon \[G7]tree.
\endchorus
\beginverse
\[Am]I'm sitting here, I \[Em]miss the power.
\[Am]I'd like to go out, \[Em]taking a shower,
\[Am]But there's a heavy \[Em]cloud inside my head.
\[Am]I feel so tired, put my\[Em]self into bed,
\[Dm]Where nothing ever \[Em]happens and I \[Am]wonder.
\endverse
\beginverse*
\[E]Isolation, \[Am]is not good for me.
\[G]Isolation, \[C]I don't want to \[E]sit on a lemon tree.
\endverse*
\beginverse
\[Am]I'm stepping around in a \[Em]desert of joy.
\[Am]Baby, anyhow I'll get a\[Em]nother toy.
\[Dm]And everything will \[Em]happen and you \[Am]wonder.
\endverse
\endsong

\beginsong{Heal the world}[by={Michael Jackson}]
\beginverse
\[A]There's a place in your \[Bm7]heart
And I \[C#m]know that it is \[Bm7/E]love
And this \[A]place could be much \[Bm7]brighter than to\[C#m]mor\[Bm7/E]row
And if \[A]you really \[Bm7]try
You'll \[C#m]find there's no need to \[Bm7/E]cry
In this \[A]place you'll feel there's \[Bm7]no hurt or \[C#m]sor\[Bm7/E]row
\endverse
\beginverse*
There are \[Bm7]ways to get \[C#m]there
If you \[D]care enough for the \[C#m]living
Make a \[Bm7]little space,
\[D/E]Make a better \[E]place.
\endverse*
\beginchorus
\[A]Heal the world, make it a \[Bm7]better place
\[Bm7/E]For you and for \[E]me and the \[A]entire human race.
\[E/G#]There are \[F#m]people \[C#m]dying,
If you \[D]care enough for the \[C#m]living,
Make a \[Bm7]better place for \[D/E]you and for \[A]me.
\endchorus
\beginverse
\[A]If you want to \[Bm7]know why
There's a \[C#m]love that cannot \[Bm7/E]lie
\[A]Love is strong, it \[Bm7]only cares for \[C#m]joyful \[Bm7/E]giving
If \[A]we try, we shall \[Bm7]see
In this \[C#m]bliss we cannot \[Bm7/E]feel
\[A]Fear or \[Bm7]dread, we stop ex\[C#m]isting and start \[Bm7/E]living
\endverse
\beginverse
\[A]We could fly so \[Bm7]high
Let our \[C#m]spirits never \[Bm7/E]die
In my \[A]heart I feel you \[Bm7]are all my \[C#m]bro\[Bm7/E]thers
Create a \[A]world with no \[Bm7]fear
Together \[C#m]we'll cry happy \[Bm7/E]tears
See the \[A]nations turn their \[Bm7]swords into \[C#m]plow\[Bm7/E]shares
\endverse
\beginverse*
And the \[G]dream we were conceived in
Will re\[A]veal a joyful face
And the \[G]world we once believed in
Will \[A]shine again in grace
Then \[F#m]why do we keep \[C#m]strangling life,
\[D]Wound this earth, crucify this \[C#m]soul?
Though it's \[Bm7]plain to see this world is heavenly,
\[D/E]Be God's \[E]glow.
\endverse*
\endsong

\beginsong{Viva la vida}[by={Coldplay}]
\textnote{Capo 1}
\beginverse
\[C]I used to \[Dadd11]rule the world
\[G]Seas would rise when I gave the \[Em]word
\[C]Now in the morning I \[Dadd11]sleep alone
\[G]Sweep the streets I used to \[Em]own
\endverse
\beginverse
\[C]I used to \[Dadd11]roll the dice
\[G]Feel the fear in my \[Em]enemy's eyes
\[C]Listen as the \[Dadd11]crowd would sing:
\[G]``Now the old king is dead! Long live the \[Em]king!''
\[C]One minute I \[Dadd11]held the key
\[G]Next the walls were \[Em]closed on me
\[C]And I discovered that my \[Dadd11]castles stand
\[G]Upon pillars of salt and \[Em]pillars of sand
\endverse
\beginchorus
\[C]I hear Jerusalem \[Dadd11]bells are ringing
\[G]Roman Cavalry \[Em]choirs are singing
\[C]Be my mirror, my \[Dadd11]sword and shield
My \[G]missionaries in a \[Em]foreign field
\[C]For some reason I \[Dadd11]can't explain
\[G]Once you'd gone there was \[Em]never,
Never an \[C]honest \[Dadd11]word
And that was \[Bm]when I ruled the \[Em]world
\endchorus
\beginverse
\[C]It was the wicked and \[Dadd11]wild wind
\[G]Blew down the doors to \[Em]let me in
\[C]Shattered windows and the \[Dadd11]sound of drums
\[G]People couldn't believe what \[Em]I'd become
\[C]Revolutionaries \[Dadd11]wait
\[G]For my head on a \[Em]silver plate
\[C]Just a puppet on a \[Dadd11]lonely string
\[G]Oh, who would ever want to be \[Em]king?
\endverse
\endsong

\beginsong{Riptide}[by={Vance Joy}]
\textnote{Capo 1}
\beginverse
\[Am]I was scared of \[G]dentists and the \[C]dark
\[Am]I was scared of \[G]pretty girls and \[C]starting conversations
\[Am]Oh, all my \[G]friends are turning \[C]green
\[Am]You're the magi\[G]cian's assistant \[C]in their dreams
\endverse
\beginverse*
A-\[Am]ooh, \[G]ooh, \[C]ooh
A-\[Am]oh, ohoh, and they \[G]come un\[C]stuck
\endverse*
\beginchorus
\[Am]Lady, \[G]running down to the \[C]riptide, taken away
To the \[Am]dark side, \[G]I wanna be your \[C]left hand man
\[Am]I love you \[G]when you're singing that \[C]song, and I got a lump
In my \[Am]throat, 'cause \[G]you're gonna sing the \[C]words wrong
\endchorus
\beginverse
\[Am]There's this movie \[G]that I think you'll \[C]like
\[Am]This guy decides to \[G]quit his job and \[C]heads to New York City
\[Am]This cowboy's \[G]running from him\[C]self
\[Am]And she's been living \[G]on the highest \[C]shelf
\endverse
\beginverse
\[Am]I just wanna, \[G]I just wanna know
\[C]If you're gonna, \[Fmaj7]if you're gonna stay
\[Am]I just gotta, \[G]I just gotta know
\[C]I can't have it, \[Fmaj7]I can't have it any other way
\endverse
\beginverse*
\[Am]I swear she's \[G]destined for the \[C]screen
\[Am]Closest thing to \[G]Michelle Pfeiffer that you've \[C]ever seen, oh
\endverse*
\endsong

\beginsong{This is the life}[by={Amy Macdonald}]
\textnote{Capo 4}
\beginverse
\[Am]Oh the wind whistles down the \[F]cold dark street tonight
\[C]And the people they were \[Em]dancing to the music vibe
\[Am]And the boys chase the girls with the curls in their hair
While the \[F]shy tormented youth sit way over there
\[C]And the songs they get louder, each one better than be\[Em]fore
\endverse
\beginchorus
\[Am]And you're singing the songs, thinking this is the life
\[F]And you wake up in the morning and your head feels twice the size
\[C]Where you gonna go? Where you gonna go?
\[Em]Where you gonna sleep tonight?
\[Am]Where you gonna sleep tonight?
\endchorus
\beginverse
\[Am]So you're heading down the road in your taxi for four
\[F]And you're waiting outside Jimmy's front door
\[C]But nobody's in and nobody's home till \[Em]four
\[Am]So you're sitting there with nothing to do
\[F]Talking about Robert Riger and his motley crew
\[C]And where you're gonna go and where you're gonna sleep to\[Em]night
\endverse
\endsong

\beginsong{A sky full of stars}[by={Coldplay}]
\textnote{Capo 6}
\beginverse
\[Am]'Cause you're a sky, \[F]'cause you're a sky full of \[C]stars \[Em]
\[Am]I'm gonna give you my \[F]heart \[C] \[Em]
\[Am]'Cause you're a sky, \[F]'cause you're a sky full of \[C]stars \[Em]
\[Am]'Cause you light up the \[F]path \[C] \[Em]
\endverse
\beginchorus
\[Am]I don't care, go on and \[F]tear me a\[C]part \[Em]
\[Am]I don't care if you \[F]do \[C] \[Em]
\[Am]'Cause in a sky, \[F]'cause in a sky full of \[C]stars \[Em]
\[Am]I think I saw \[F]you \[C] \[Em]
\endchorus
\beginverse
\[Am]'Cause you're a sky, \[F]'cause you're a sky full of \[C]stars \[Em]
\[Am]I wanna die in your \[F]arms, oh \[C] \[Em]
\[Am]'Cause you get lighter the \[F]more it gets \[C]dark \[Em]
\[Am]I'm gonna give you my \[F]heart \[C] \[Em]
\endverse
\beginverse
\[F]Because you're a sky, \[G]you're a sky full of \[Am]stars \[C]
Such a \[F]heavenly \[G]view \[Am] \[C]
\endverse
\endsong

\beginsong{Here comes the sun}[by={The Beatles}]
\textnote{Capo 7}
\beginchorus
\[D]Here comes the sun (doo doo doo doo)
\[G]Here comes the \[E7]sun
And I \[D]say, it's alright
\endchorus
\beginverse
\[D]Little darling, it's been a \[G]long cold lonely \[A7]winter
\[D]Little darling, it \[G]feels like years since it's been \[A7]here
\endverse
\beginverse
\[D]Little darling, the \[G]smiles returning to the \[A7]faces
\[D]Little darling, it \[G]seems like years since it's been \[A7]here
\endverse
\beginverse*
\[F]Sun, \[C]sun, \[G/B]sun, \[G]here it \[D]comes \[A7]
\endverse*
\beginverse
\[D]Little darling, I \[G]feel that ice is slowly \[A7]melting
\[D]Little darling, it \[G]seems like years since it's been \[A7]clear
\endverse
\endsong

\beginsong{Another love}[by={Tom Odell}]
\beginverse
\[C]I wanna take you \[Em]somewhere so you \[Am]know I \[Em]care,
But it's so \[Bm]cold and I don't know \[C]where.
I brought you \[Em]daffodils, on a \[Am]pretty \[Em]string,
But they won't \[Bm]flower like they did last \[C]spring.
\[C]And I wanna \[Em]kiss you, make you \[Am]feel al\[Em]right,
But I'm just so \[Bm]tired to share my \[C]nights.
I wanna \[Em]cry and I \[Am]wanna \[Em]love
But all my \[Bm]tears have been used \[C]up.
\endverse
\beginchorus
\[C]On another \[G]love, another \[Em]love,
All my \[Bm]tears have been used \[C]up,
On another \[G]love, another \[Em]love,
All my \[Bm]tears have been used \[C]up,
On another \[G]love, another \[Em]love,
All my \[Bm]tears have been used \[C]up. \[G]
\endchorus
\beginverse
\[C]And if somebody \[Em]hurts you, yeah I \[Am]wanna \[Em]fight,
But my hands been \[Bm]broken one too many \[C]times.
So I use my \[Em]voice, I'll be so \[Am]fucking \[Em]rude,
Words they always \[Bm]win, but I know I'll \[C]lose.
And I'd sing a \[Em]song that would be \[Am]just \[Em]ours,
But I sang 'em \[Bm]all to another \[C]heart.
And I wanna \[Em]cry I wanna \[Am]learn to \[Em]love,
But all my \[Bm]tears have been used \[C]up.
\endverse
\beginverse
\[C]I wanna sing a \[Em]song that would be \[Am]just \[Em]ours,
But I sang 'em \[Bm]all to another \[C]heart.
And I wanna \[Em]cry I wanna \[Am]fall in \[Em]love,
But all my \[Bm]tears have been used \[C]up.
\endverse
\endsong

\end{songs}\songcolumns{2}\begin{songs}{titleidx}

\beginsong{We are the champions}[by={Queen}]
\beginverse
\[Cm]I've paid my \[Gm7/C]dues,
\[Cm]Time after \[Gm7/C]time.
\[Cm]I've done my \[Gm7/C]sentence
\[Cm]But committed no \[Gm7/C]crime.
\[Eb]And bad mis\[Ab/Eb]takes,
\[Eb]I've made a \[Ab/Eb]few.
\[Eb]I've had my share of \[Bb/D]sand kicked in my \[Cm]face
But \[F7]I've come \[Bb]through.
And I mean to go \[Ab/Bb]on, and \[Bbm7b5]on, and \[Bb7]on, and \[C7]on.
\endverse
\beginchorus
\[F]We are the \[Am]champions, my \[Dm]friends, \[Bb] \[C7]
\[F]And we'll keep on \[Am]fighting till the \[Bb]end. \[F#dim7]
\[Gm7]We are the \[C7/G]champions, \[Bbm6]we are the \[Bbm6/Db]cham\[Edim7]pi\[Gdim7]ons.
\[F]No time for \[Ebadd9/G]losers 'cause \[Ab6]we are the \[Bb]cham\[Cm7add4]pions
Of the \[Fm]world. \[Gm7] \[Fm] \[Gm7/C]
\endchorus
\beginverse
\[Cm]I've taken my \[Gm7/C]bows
\[Cm]And my curtain \[Gm7/C]calls.
\[Cm]You brought me fame and fortune and \[Gm7/C]everything that goes with it,
\[Cm]I thank you \[Gm7/C]all.
\[Eb]But it's been no bed of \[Ab/Eb]roses,
\[Eb]No pleasure \[Ab/Eb]cruise.
\[Eb]I consider it a challenge be\[Bb/D]fore the whole human \[Cm]race
And \[F7]I ain't gonna \[Bb]lose.
And I mean to go \[Ab/Bb]on, and \[Bbm7b5]on, and \[Bb7]on, and \[C7]on.
\endverse
\endsong

\beginsong{Zombie}[by={The Cranberries}]
\beginverse
\[Em]Another \[C]head hangs lowly, \[G]child is slowly \[D/F#]taken
\[Em]And the violence \[C]caused such silence, \[G]who are we mis\[D/F#]taken?
\[Em]But you see, it's \[C]not me, it's not \[G]my family
In your \[D/F#]head, in your head they are fighting
\[Em]With their tanks \[C]and their bombs, \[G]and their bombs and their \[D/F#]guns
\[Em]In your head, \[C]in your head, they are \[G]crying \[D/F#]
\endverse
\beginchorus
\[Em]In your \[C]head, in your \[G]head
Zombie, \[D/F#]zombie, zombie-ie-ie
\[Em]What's in your \[C]head, in your \[G]head
Zombie, \[D/F#]zombie, zombie-ie-ie-ie
\endchorus
\beginverse
\[Em]Another \[C]mother's breakin' \[G]heart is taken \[D/F#]over
\[Em]When the violence \[C]causes silence \[G]we must be mis\[D/F#]taken
\[Em]It's the same old \[C]theme since \[G]nineteen-sixteen
In your \[D/F#]head, in your head they're still fighting
\[Em]With their tanks \[C]and their bombs, \[G]and their bombs and their \[D/F#]guns
\[Em]In your head, \[C]in your head, they are \[G]dying \[D/F#]
\endverse
\endsong

\beginsong{Forever Young}[by={Alphaville}]
\beginverse
\[C]Let's dance in style, \[G]let's dance for a while,
\[Am]Heaven can wait we're only \[F]watching the \[G]skies.
Hoping for the \[Dm]best, but expecting the \[F]worst,
Are you gonna drop the \[G6]bomb \[Fmaj7]or \[G6]not? \[C]
\[C]Let us die young \[G]or let us live for\[Am]ever,
We \[F]don't have the power, but we \[G]never say never.
Sitting in the \[Dm]sandpit, life is a short \[F]trip,
The music's for the \[G6]sad \[Fmaj7]man. \[G6] \[C]
\endverse
\beginchorus
\[C]Forever \[G]Young,
I want to be \[Am]Forever \[F]Young.
\[G]Do you really want to \[Am]live forever?
\[F]Forever, \[G]and ever.
\[C]Forever \[G]Young,
I want to be \[Am]Forever \[F]Young.
\[G]Do you really want to \[Am]live forever?
\[F]For\[G]ever \[C]Young.
\endchorus
\beginverse
\[C]Some are like water, \[G]some are like the heat,
\[Am]Some are the melody and \[F]some are the \[G]beat.
Sooner or later \[Dm]they all will be \[F]gone,
Why don't they stay \[G6]yo\[Fmaj7]ung? \[G6] \[C]
\[C]It's so hard to get \[G]old without a cause,
\[Am]I don't want to perish \[F]like a fading \[G]horse.
Youth's like \[Dm]diamonds in the \[F]sun,
And diamonds are for\[G6]e\[Fmaj7]ver. \[G6] \[C]
\endverse
\endsong

\beginsong{The Sound of Silence}[by={Simon \& Garfunkel}]
\textnote{Capo 6}
\beginverse
\[Am]Hello darkness, my old \[G]friend,
I've come to talk with you a\[Am]gain,
Because a vision softly \[F]cree\[C]ping,
Left its seeds while I was \[F]slee\[C]ping,
And the \[F]vision that was planted in my \[C]brain
Still re\[C/B]mains \[Am] \[C]
Within the \[G]sound of \[Am]silence.
\endverse
\beginverse
In restless dreams I walked a\[G]lone,
Narrow streets of cobble\[Am]stone.
'Neath the halo of a \[F]street \[C]lamp,
I turned my collar to the \[F]cold and \[C]damp.
When my \[F]eyes were stabbed by the flash of a neon \[C]light
That split the \[C/B]night \[Am] \[C]
And touched the \[G]sound of \[Am]silence.
\endverse
\beginverse
And in the naked light I \[G]saw
Ten thousand people, maybe \[Am]more.
People talking without \[F]spea\[C]king,
People hearing without \[F]liste\[C]ning,
People \[F]writing songs that voices never \[C]share
And no one \[C/B]dare \[Am] \[C]
Disturb the \[G]sound of \[Am]silence.
\endverse
\beginverse
Fools said I, you do not \[G]know
Silence like a cancer \[Am]grows.
Hear my words that I might \[F]teach \[C]you,
Take my arms that I might \[F]reach \[C]you.
But my \[F]words like silent raindrops \[C]fell, \[C/B] \[Am]
And \[C]echoed in the \[G]wells of \[Am]silence.
\endverse
\beginverse
And the people bowed and \[G]prayed
To the neon god they \[Am]made.
And the sign flashed out its \[F]war\[C]ning,
In the words that it was \[F]for\[C]ming.
And the \[F]sign said, the words of the prophets
Are written on the subway \[C]walls
And tenement \[C/B]halls \[Am]
And \[C]whisper'd in the \[G]sounds of \[Am]silence.
\endverse
\endsong
