\beginsong{Lemon Tree}[by={Fool's Garden}]
\textnote{Capo 8}
\beginverse
\[Am]I'm sitting here in a \[Em]boring room,
\[Am]It's just another rainy \[Em]Sunday afternoon.
\[Am]I'm wasting my time, I got \[Em]nothing to do.
\[Am]I'm hanging around, I'm \[Em]waiting for you,
\[Dm]But nothing ever \[Em]happens and I \[Am]wonder.
\endverse
\beginverse
\[Am]I'm driving around in my \[Em]car,
\[Am]I'm driving too fast, I'm \[Em]driving too far.
\[Am]I'd like to change my \[Em]point of view,
\[Am]I feel so lonely, I'm \[Em]waiting for you,
\[Dm]But nothing ever \[Em]happens and I \[Am]wonder.
\endverse
\beginchorus
\[C]I wonder how, I wonder \[G]why,
\[Am]Yesterday you told me 'bout the \[Em]blue blue sky
\[F]And all that I can \[G]see is just a yellow \[C]lemon \[G7]tree.
\[C]I'm turning my head, up \[G]and down,
\[Am]I'm turning, turning, turning, turning, \[Em]turning around
\[F]And all that I can \[F#dim7]see is just another \[G]lemon \[G7]tree.
\endchorus
\beginverse
\[Am]I'm sitting here, I \[Em]miss the power.
\[Am]I'd like to go out, \[Em]taking a shower,
\[Am]But there's a heavy \[Em]cloud inside my head.
\[Am]I feel so tired, put my\[Em]self into bed,
\[Dm]Where nothing ever \[Em]happens and I \[Am]wonder.
\endverse
\beginverse*
\[E]Isolation, \[Am]is not good for me.
\[G]Isolation, \[C]I don't want to \[E]sit on a lemon tree.
\endverse*
\beginverse
\[Am]I'm stepping around in a \[Em]desert of joy.
\[Am]Baby, anyhow I'll get a\[Em]nother toy.
\[Dm]And everything will \[Em]happen and you \[Am]wonder.
\endverse
\endsong
