\beginsong{Lemon Tree}[by={Fool's Garden}]
\textnote{Capo 8}
\beginverse
I'm \[Am]sitting here in a \[Em]boring room,
It's \[Am]just another rainy Sunday \[Em]afternoon.
I'm \[Am]wasting my time, I got \[Em]nothing to do.
I'm \[Am]hanging around, I'm \[Em]waiting for you,
But \[Dm]nothing ever \[Em]happens and I \[Am]wonder. \[Em] \[Am]
\endverse
\beginverse
I'm \[Am]driving around \[Em]in my car,
I'm \[Am]driving too fast, I'm \[Em]driving too far.
I'd \[Am]like to change my \[Em]point of view,
I \[Am]feel so lonely, I'm \[Em]waiting for you,
But \[Dm]nothing ever \[Em]happens and I \[Am]wonder. \[Em] \[Am]
\endverse
\beginchorus
I \[C]wonder how, I \[G]wonder why,
\[Am]Yesterday you told me 'bout the \[Em]blue blue sky
And \[F]all that I can \[G]see is just a yellow \[C]lemon tree. \[G7]
I'm \[C]turning my head, \[G]up and down,
I'm \[Am]turning, turning, turning, turning, \[Em]turning around
And \[F]all that I can \[F#dim7]see is just another \[G]lemon tree. \[G7]
\endchorus
\beginverse
I'm \[Am]sitting here, I \[Em]miss the power.
I'd \[Am]like to go out, ta\[Em]king a shower,
But \[Am]there's a heavy cloud \[Em]inside my head.
I \[Am]feel so tired, put my\[Em]self into bed,
Where \[Dm]nothing ever \[Em]happens and I \[Am]wonder. \[Em] \[Am]
\endverse
\beginverse*
\[E]Isolation, \[Am]is not good for me.
\[G]Isolation, \[C]I don't want to \[E]sit on a lemon tree.
\endverse
\beginverse
I'm \[Am]stepping around in a \[Em]desert of joy.
\[Am]Baby, anyhow I'll get \[Em]another toy.
And \[Dm]everything will \[Em]happen and you \[Am]wonder. \[Em] \[Am]
\endverse
\endsong
