\beginsong{Another love}[by={Tom Odell}]
\beginverse
\[C] I wanna take you \[Em]somewhere so you \[Am]know I \[Em]care,
But it's so \[Bm]cold and I don't know \[C]where.
I brought you \[Em]daffodils, on a \[Am]pretty str\[Em]ing,
But they won't \[Bm]flower like they did la\[C]st spring. \[C]
\[C] And I wanna \[Em]kiss you, make you \[Am]feel al\[Em]right,
But I'm just so \[Bm]tired to share my \[C]nights.
I wanna \[Em]cry and I \[Am]wanna \[Em]love
But all my \[Bm]tears have been used \[C]up. \[C]
\endverse
\beginchorus
\[C] On another love\[G], another love,\[Em]
All my \[Bm]tears have been used \[C]up,
On another love\[G], another lo\[Em]ve,
All my \[Bm]tears have been used \[C]up,
On another lo\[Em]ve, another love,\[Em]
All my \[Bm]tears have been used \[C]uuhuuuuh\[G]uuup. 
\endchorus
\beginverse
\[C]And if somebody \[Em]hurts you, yeah I \[Am]wanna \[Em]fight,
But my hands been \[Bm]broken one too many \[C]times.
So I use my \[Em]voice, I'll be so \[Am]fucking \[Em]rude,
Words they always \[Bm]win, but I know I'll \[C]lose.
And I'd sing a \[Em]song that would be \[Am]just \[Em]ours,
But I sang 'em \[Bm]all to another \[C]heart.
And I wanna \[Em]cry I wanna \[Am]learn to \[Em]love,
But all my \[Bm]tears have been used \[C]up.
\[Em]Oooh\[Bm]oooh
\endverse
\beginverse
\[C ]I wanna sing a \[Em]song that would \[Am]be just \[Em]ours,
But I sang 'em \[Bm]all to another \[C]heart.
And I wanna \[Em]cry I wanna \[Am]fall in \[Em]love,
But all my \[Bm]tears have been used \[C]up.
\endverse
\endsong
