\beginsong{Forever Young}[by={Alphaville}]
\beginverse
\[C] Let's dance in sty\[G]le, let's dance for a \[Am]while,
Heaven can \[F]wait we're only watching the \[G]skies.
Hoping for the \[Dm]best, but expecting the \[F]worst,
Are you gonna drop the \[G6]bomb \[Fmaj7]or not?\[G6] \[C]
\[C]Let us die \[G]young or let us live for\[Am]ever,
We don't ha\[F]ve the power, but we never \[G]say never.
Sitting in the \[Dm]sandpit, life is a short \[F]trip,
The music's for the sad \[G6]man. \[Fmaj7]  \[G6] \[C]
\[C]Can you imagine \[G]when this race is won\[Am]
Turn our \[F]golden faces into the sun\[G]
Praising our l\[Dm]eaders, we're getting in \[F]tune
The music's played by \[G6] the ma\[Fmaj7]d man.\[G6] \[C]
\endverse
\beginchorus
\[C] Forever \[G]Young,
I want to \[Am]be Forever \[F]Young.
\[G] Do you really want to \[Am]live forever?
\[F] Forever,\[G] and ever.
\[C] Forever \[G]Young,
I want to \[Am]be Forever \[F]Young.
\[G]Do you really want to \[Am]live forever?
\[F] \[G] Forever \[C]Young.
\endchorus
\beginverse
\[C]Some are like wa\[G]ter, some are like the \[Am]heat,
Some are t\[F]he melody and some are the \[G]beat.
Sooner or later\[Dm] they all will be gone,\[F]
Why don't they stay yo\[G6]ung? \[Fmaj7] \[G6] \[C]
\[C]It's so hard to \[G]get old without a cause,\[Am]
I don't wa\[F]nt to perish like a fading hor\[G]se.
Youth's like dia\[Dm]monds in the sun,\[F]
And diamonds are fore\[G6]ver. \[Fmaj7] \[G6] \[C]
\[C]So many adventur\[G]es given up today \[Am]
So many son\[F]gs we forgot to play \[G]
So many dreams \[Dm]swinging out of the blue\[F]
Oh let it come true  \[G6] \[Fmaj7] \[G6] \[C]
\endverse
\endsong
