\beginsong{The Sound of Silence}[by={Simon \& Garfunkel}]
\textnote{Capo 6}
\beginverse
\[Am] Hello darkness, my old \[G]friend,
I've come to talk with you a\[Am]gain,
Because a vision soft\[F]ly cree\[C]ping,
Left its seeds while I \[F]was slee\[C]ping,
And the \[F]vision that was planted in my \[C]brain
Still remai\[C/B]ns \[Am] \[C]
Within the \[G]sound of \[Am]silence.
\endverse
\beginverse
In restless dreams I walked a\[G]lone,
Narrow streets of cobble\[Am]stone.
'Neath the halo of a \[F]street \[C]lamp,
I turned my collar to the \[F]cold and \[C]damp.
When my \[F]eyes were stabbed by the flash of a neon \[C]light
That split the night\[C/B] \[Am] \[C]
And touched the \[G]sound of \[Am]silence.
\endverse
\beginverse
And in the naked light I \[G]saw
Ten thousand people, maybe \[Am]more.
People talking with\[F]out spea\[C]king,
People hearing with\[F]out liste\[C]ning,
People writing \[F]songs that voices never \[C]share
And no one dare\[C/B] \[Am] \[C]
Disturb the \[G]sound of \[Am]silence.
\endverse
\beginverse
Fools said I, you do not \[G]know
Silence like a cancer \[Am]grows.
Hear my words that I \[F]might teach \[C]you,
Take my arms that I \[F]might reach \[C]you.
But my \[F]words like silent raindrops \[C]fell, \[C/B] \[Am]
And \[C]echoed in the \[G]wells of \[Am]silence.
\endverse
\beginverse
And the people bowed and \[G]prayed
To the neon god they \[Am]made.
And the sign flashed out \[F]its war\[C]ning,
In the words that it \[F]was for\[C]ming.
And the sign said, the \[F]words of the prophets
Are written on the subway \[C]walls
And tenement halls \[C/B]\[Am]
And \[C]whisper'd in the \[G]sounds of \[Am]silence.
\endverse
\endsong
