\beginsong{The Partisan}[by={Leonard Cohen}]
\beginverse
\[Am]When they \[C]poured a\[E]cross the \[Am]border
I was \[C]cautioned \[E]to sur\[Am]render,
This I \[C]could not \[G]do;
\[F] I took my \[F]gun and van\[C]ished. \[E] \[Am]
\endverse
\beginverse
\[Am]I have \[C]changed my \[E]name so \[Am]often,
I've \[C]lost my \[E]wife and \[Am]children
But I have \[C]many fri\[G]ends,
\[F] And some \[F]of them are with \[C]me. \[E] \[Am]
\endverse
\beginverse
\[Am]An old \[C]woman \[E]gave us \[Am]shelter,
Kept us \[C]hidden \[E]in the \[Am]garret,
Then the \[C]soldiers \[G]came;
\[F] She died \[F]without a whis\[C]per. \[E] \[Am]
\endverse
\beginverse
\[Am]There were \[C]three of \[E]us this \[Am]morning,
I'm the \[C]only \[E]one this \[Am]evening
But I \[C]must go \[G]on;
\[F] The front\[F]iers are my pri\[C]son. \[E] \[Am]
\endverse
\beginverse
\[Am]Oh, the \[C]wind, the \[E]wind is \[Am]blowing,
Through the \[C]graves the \[E]wind is \[Am]blowing,
Freedom \[C]soon will \[G]come;
\[F] Then we'll \[F]come from the shad\[C]ows. \[E] \[Am]
\endverse
\beginverse
\[Am]Les Alle\[C]mands é\[E]taient chez \[Am]moi,
Ils me \[C]dirent : ``Ré\[E]signe \[Am]toi,''
Mais je \[C]n'ai pas \[G]peur; \[G]
\[F] J'ai \[F]repris mon ar\[C]me. \[E] \[Am]
\endverse
\beginverse
\[Am]J'ai chan\[C]gé cent \[E]fois de \[Am]nom,
J'ai per\[C]du femme \[E]et en\[Am]fants
Mais j'ai \[C]tant d'a\[C]mis;
\[F] J'ai la France en\[C]tière. \[E] \[Am]
\endverse
\beginverse
\[Am]Un vieil \[C]homme dans \[E]un gre\[Am]nier
Pour la \[C]nuit nous \[E]a ca\[Am]chés,
Les Alle\[C]mands l'ont \[G]pris;
\[F] Il est \[F]mort sans sur\[C]pri\[E]se. \[Am]
\endverse
\beginverse
\[Am]Oh, the \[C]wind, the \[E]wind is \[Am]blowing,
Through the \[C]graves the \[E]wind is \[Am]blowing,
Freedom \[C]soon will \[G]come;
\[F] Then we'll \[F]come from the shad\[C]ows. \[E] \[Am]
\endverse
\endsong
